Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-21 longoutput.tex
Fix bug
Fix wording
Start typing ground state checking algorithm
Rewrite ground state check theorem statement

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$, and $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$. The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
	\end{itemize}
\end{theorem}

@@

We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
\begin{itemize}
	\item $C'$ uses only Hadamard and Toffoli gates.
	\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
	\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple to verify that $F$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
\end{proof}

@@

\begin{theorem}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$
	with ground state $\psi$ with the following properties:
	\begin{itemize}
		\item $\braket{\psi|H|\psi}=0$
		\item $\forall{\ket\phi}, \braket{\psi|\phi}=0\Rightarrow\braket{\phi|H|\phi}\geq\frac{3}{4}$
		\item has $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	\end{itemize}
	Then there exists an algorithm that accepts $\ket\psi$ with probabily $\frac{1}{2}$. Furthermore, for $\ket\phi$ where $\braket{\psi|\phi}=0$, it accepts with probability at most $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})$. This algorithm doesn't apply any quantum gates, and performs only $X$ and $Z$ measurements on the input state.
\end{theorem}
\begin{proof}

@@

We scale the Hamiltonian.
$$D=\sum_{S\in\mathcal{G}_{XZ}}|d_S|$$
$$p_S=\frac{|d_S|}{D}=O(\poly(T))$$
$$H'=\frac{H}{D}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)S$$

Note that $H'$ is now a weighted sum of measurement operators. We also have $0\leq p_S\leq1$ and $\sum_{S\in\mathcal{G}_{XZ}} p_S=1$, so we can treat it as a probability distribution over the choice of $S$.
$$\braket{\phi|H'|\phi}=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}=\E_S[\sgn(d_S)\braket{\phi|S|\phi}]$$
Which is simple to estimate by picking and doing the measurements corresponding to $S$. The measurement result is $\pm1$. It can be modeled as a Bernoulli distribution with known expected value. The rest is simple number crunching.

TODO Above is NOT just simple number crunching. Type it out.
\end{proof}

>>>>

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of $T$ gates, each either $H$ or $\Lambda(P(i))$.
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x||0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$. The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
	\end{itemize}
\end{theorem}

@@

We construct $C'$ so that $\mathcal{F}\circ C=C'\circ\mathcal{F}$ by following the computation above. It satisfies the required properties by construction.
\begin{itemize}
	\item $C'$ uses only Hadamard and Toffoli gates.
	\item Exchanging $\mathcal{F}$ with $H$ doesn't change the circuit size. Exchanging $\mathcal{F}$ with controlled phase gate turns it into $4$ gates. So the final result is at most $4T$ gates.
	\item When $x$ is classical, $\mathcal{F}(x)=x||0$. So $F\circ C(x)=C'(x||0)$. It is simple to verify that $F$ preserves $X$ and $Z$ measurement results on the first $n$ qubits.
\end{itemize}
\end{proof}

@@

\begin{theorem}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$ with  $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	Then there exists an algorithm that accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. This algorithm performs only $X$ and $Z$ measurements on $\ket\phi$, and is classical otherwise.
\end{theorem}
\begin{proof}

@@

\begin{algorithm}
	\caption{Check for ground state}
	\begin{algorithmic}[1]
		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State $p_S=\frac{|d_S|}{D}$
		\State $\tilde{S}\gets$ Pick weighted using $p_S$
		\State $\lambda_{\tilde{S}}\gets$ Measure $\ket\phi$ in the $\tilde{S}$ basis
		\If{$\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$}
			\State Accept
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}

\begin{align*}
	\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
	&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\E[\lambda_{\tilde{S}}]]\\
	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]
\end{align*}

Note that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$.

$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]=-p+(1-p)$$
\begin{align*}
	\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
	&=\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}
\end{align*}

\end{proof}
